---
title: "Home work 4"
author: "Caroline Bena Kuno"
date: "March 1, 2019"
output: pdf_document
---
```{r}
library(ggplot2)
library(dplyr)
attach(infert)
ggplot(infert, aes(x =education, y =age, group =induced, color=induced)) +
  geom_point()
edu_induced <- infert%>% 
  group_by(education,induced)%>% 
  tally() 
 head(edu_induced)
 View(edu_induced)

```
```{r}
library(ggplot2)
library(dplyr)
attach(infert)
edu_induced <- infert%>% 
  group_by(education,induced)%>% 
  tally() 
ggplot(edu_induced, aes(x =education, y=n, group =induced, color=induced)) +
  geom_line() + facet_wrap(~ induced)
```

## Problem 2

**Reference**
Madigan, E. A., Curet, O. L., & Zrinyi, M.(2008).Workforce analysis using data mining and linear regression
to understand HIV/AIDS prevalence patterns.*Human resources for health, 6(1), 2.*

**Introduction** 

The purpose of the study was to examine the association between the health workforce,
particularly the nursing workforce, and the achievement of the MDGs, taking into account other factors
known to influence health status, such as socioeconomic indicators.

**Method** 

A merged data set that includes country-level MDG outcomes, workforce statistics, and general
socioeconomic indicators was utilized for the present study. Data were obtained from the Global Human
Resources for Health Atlas 2004, the WHO Statistical Information System (WHOSIS) 2000, UN Fund for
Development and Population Assistance (UNFDPA) 2000, the International Council of Nurses "Nursing in
the World", and the WHO/UNAIDS database. Two approaches were used for analysis: data mining using
classification and regression trees (CART) and standard statistical analyses using ordinary least squares
regression.

*Results and conclusion** 

The main factors in understanding HIV/AIDS prevalence rates are physician
density followed by female literacy rates and nursing density in the country. Using general linear model
approaches, increased physician and nurse density (number of physicians or nurses per population) was
associated with lower adult HIV/AIDS prevalence rate, even when controlling for socioeconomic indicators.
Increased nurse and physician density are associated with improved health outcomes,suggesting that countries
aiming to attain the MDGs related to HIV/AIDS would do well to invest in their health workforce.